% Created by Kamil Niemcewicz 
\newcommand{\rightPanel}
{
    \section{Education}
        \begin{template}
            \templateitem 	
            {2015 - 2019}
            {The Katowice Institute of Information Technologies}
            {\relax}
            {
             Specialization Program - Software Engineering
            }
        \end{template}
        
    \section{Experience}
        \begin{template}
            \templateZeroIndent	
            {Siemion.pl sp. z o.o.}
            {2014 - now}
            {
            • ERP software deployment (enova365), \\
            • programming printouts based on data (C\# ASP.NET),\\
            • software development based on API,\\
            • creating software and scripts to speed up workflow,\\
            • programming VBA scripts to speed up company processes (Word, Excel),\\
            • server administration: MS Windows: SBS 2003, Windows Server 2005 and 2016, \\
            • SQL Server administration: MS SQL Server 2008 and 2016, \\
            • network management in small company,\\
            • servers troubleshooting,\\
            • ensuring highest standards of security for corporate data and customers,\\
            • servicing hardware and software,\\
            • bookkeeping company documentation (HR, accounting, trade),\\
            • analyzing customer business issues.
            }
        \end{template}
        
    \section{Projects}
        \begin{template}

            \templateZeroIndent 
            {Books storage}
            {Java (at this moment recreating with C\# + entity framework)}
            {
                Program allows you to keep a list of books in one place with duplication control. You can store most important informations: name, author, book format, size, and ISBN. You can create user profiles so data is protected from unauthorized access. Passwords are stored in a separate file, ensuring very high security standards.
            }
            
            \templateZeroIndent 
            {Liner}
            {Python + wxPython/wxFormBuilder}
            {
                Program for matching, aligning nucleotide sequences using the Needleman-Wunsch algorithm. Allows you to load two DNA sequences, align them and display them in an easy-to-read interface.
            }
            
            \templateZeroIndent 
            {Miscellaneous}
            {C\#, JAVA, C++, VBA, Autohotkey}
            {
                Every month there is always at least a few small scripts to create, programs to be made, projects to do for my various needs, for company's clients I work with, or just among my friends.
            }
            
            \templateZeroIndent
            {\href{http://portal.bioslone.pl}{http://portal.bioslone.pl}}
            {Joomla}
            {
                I have transferred all data from CMS Drupal 5 to Joomla! 3.5 with applying all necessary changes related to the preparation and adaptation of the template to the new portal, foundation and publisher websites.
            }
            
            \templateZeroIndent 
            {Miscellaneous}
            {C\#, JAVA, C++, VBA, Autohotkey}
            {
                Every month there is always at least a few small scripts to create, programs to be made, projects to do for my various needs, for company's clients I work with, or just among my friends.
            }
        \end{template}
        
    \section{Certificates}
        \begin{template}
            \templateitem {2017} 
                {\href{https://www.udemy.com/csharp-intermediate-classes-interfaces-and-oop/\#curriculum}{Udemy - C\# Intermediate: Classes, Interfaces and OOP}}
                {\relax}
                {\relax}
                
            \templateitem {2017} 
                {\href{https://www.udemy.com/linqlinq/learn/v4/content}{Udemy - Mastering LINQ with C\# and .NET}}
                {\relax}
                {\relax}
            
        \end{template}
}